\documentclass[12pt, a4paper]{article}
\usepackage{tabularx}

\usepackage[margin=0.9in]{geometry}

\usepackage{enumitem}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{} % clear all header fields
\renewcommand{\headrulewidth}{0pt} % no line in header area
\fancyfoot{} % clear all footer fields

\fancyfoot[RE,LO]{\fontsize{8}{10} \selectfont Chair of Computer
  Science 4 Contributor Agreement 1.0 – Adapted from Open Source
  Research Group Contributor Agreement 1.0. This document is licensed
  under the CC­BY­SA 3.0 license, see
  http://creativecommons.org/licenses/by­sa/3.0/}

\setlength{\parindent}{0pt}

\begin{document}

\textbf{\large{Chair of Computer Science 4 Contributor Agreement
    v1.0}} \newline\newline These terms apply to your contribution of
materials to a product or project owned or managed by us ('project'),
and set out the intellectual property rights you grant to us (the
Chair of Computer Science 4 at the Friedrich-­Alexander University of
Erlangen­-Nuremberg represented by Prof. Dr. Wolfgang Schröder-Preikschat) in
the contributed materials. If this contribution is on behalf of a
company, the term 'you' will also mean the company you identify
below. If you agree to be bound by these terms, fill in the
information requested below and provide your signature.

Read this agreement carefully before signing.

\begin{enumerate}[leftmargin=15pt]

\item The term 'contribution' means any source code, object code,
  patch, tool, sample, graphic, specification, manual, documentation,
  or any other material posted or submitted by you to a project.

\item With respect to any worldwide copyrights, or copyright
  applications and registrations, in your contribution:
  \begin{itemize}[leftmargin=15pt]
  \item you hereby assign to us joint ownership, and to the extent
    that such assignment is or becomes invalid, ineffective or
    unenforceable, you hereby grant to us a perpetual, irrevocable,
    non­exclusive, worldwide, no­charge, royalty­free, unrestricted
    license to exercise all rights under those copyrights. This
    includes, at our option, the right to sublicense these same rights
    to third parties through multiple levels of sublicensees or other
    licensing arrangements;
  \item you agree that each of us can do all things in relation to
    your contribution as if each of us were the sole owners, and if
    one of us makes a derivative work of your contribution, the one
    who makes the derivative work (or has it made) will be the sole
    owner of that derivative work;
  \item you agree that you will not assert any moral rights in your
    contribution against us, our licensees or transferees;
  \item you agree that we may register a copyright in your
    contribution and exercise all ownership rights associated with it;
    and
  \item you agree that neither of us has any duty to consult with,
    obtain the consent of, pay or render an accounting to the other
    for any use or distribution of your contribution.
  \end{itemize}

\item With respect to any patents you own, or that you can license
  without payment to any third party, you hereby grant to us a
  perpetual, irrevocable, non­exclusive, worldwide, no­ charge,
  royalty­free license to:

  \begin{itemize}[leftmargin=15pt]
  \item make, have made, use, sell, offer to sell, import, and
    otherwise transfer your contribution in whole or in part, alone or
    in combination with or included in any product, work or materials
    arising out of the project to which your contribution was
    submitted, and
  \item at our option, to sublicense these same rights to third
    parties through multiple levels of sublicensees or other licensing
    arrangements.
  \end{itemize}

\item Except as set out above, you keep all right, title, and interest
  in your contribution. The rights that you grant to us under these
  terms are effective on the date you first submitted a contribution
  to us, even if your submission took place before the date you sign
  these terms. Any contribution we make available under any license
  will also be made available under a suitable FSF (Free Software
  Foundation) or OSI (Open Source Initiative) approved license.

\item With respect to your contribution, you represent that:
  \begin{itemize}[leftmargin=15pt]
  \item it is an original work and that you can legally grant the
    rights set out in these terms;
  \item it does not to the best of your knowledge violate any third
    party's copyrights, trademarks, patents, or other intellectual
    property rights; and
  \item you are authorized to sign this contract on behalf of your
    company (if identified below).
  \end{itemize}

\item These terms will be governed by the laws of Germany. Any choice
  of law rules will not apply.
\end{enumerate}

If available, please list your username(s) and the name of the
project(s) (or project website(s)) for which you would like to
contribute materials.\newline
\begin{tabularx}{\textwidth}{|X|}
  \hline
  \\
  Username:\\
  \\
  \hline
  \\
  Project name (or project website):\\
  \\
  \hline
\end{tabularx}
Your contact information (Please print clearly):\newline
\begin{tabularx}{\textwidth}{|X|l}
  \hline
  \\
  Your name:\\
  \\
  \hline
  \\
  Mailing address:\\
  \\
  \hline
  \\
  Telephone:\\
  Email:\\
  \\
  \hline
  \\
  Your signature:\\
  \\
  \hline
  \\
  Date:\\
  \\
  \hline

\end{tabularx}

To deliver these terms to us, scan and email, or fax a signed copy to
us using the email address or fax number set out on the appropriate
project website.

\end{document}